Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-20 draft.tex
grammar fixes for first paragraph

\section*{Introduction}
There is a replication crisis in Science. It has recently been highlighted in
medicine \citep{ioannidis:2005}, psychology \citep{nosek:2015}, the
political sciences \citep{janz:2015}, and even more recently in the biomedical
sciences \citep{iqbal:2016}. The reasons for such non-reproducibility are as
diverse as these domains are. In medicine, the {\em study power and bias, the
number of other studies on the same question, and, importantly, the ratio of
true to no relationships among the relationships probed in each scientific
field} are important causes, as reported by \citep{ioannidis:2005}. In psychology,
the infamous p-value seems to be the root of all evil, while in the biomedical
sciences, \citep{iqbal:2016} identified a {\em lack of access to full datasets and
detailed protocols for both clinical and non-clinical biomedical
investigation}. Surprisingly enough, the computational sciences (in the broad
sense) and computer sciences are no exception, even though they rely mostly on
code and data that are believed to be not prone to the aforementioned
problems.\\

When \citep{collberg:2014, collberg:2015} decided to measure the
extent of the problem precisely, they investigated the availability of code and data,
and {\em the extent to which this code would actually build with reasonable
  effort}. The results were dramatic: of the 515 potentially reproducible
papers (out of 613) targeted by the study, the authors managed to ultimately run
only 102, i.e. less than 20\%. It is to be underlined that the authors only
investigated the possibility to run the code. They did not check for the
correctness of the code (does the code actually implement what is advertised
in the paper), nor the replicability of the results (does the run lead to the
same results as in the paper).  \citep{topalidou:2015a} encountered the same
problem when they tried to replicate a model from the computational
neuroscience literature: source code was not part of the supplementary section
of the paper and no link or repository was provided in the main text. When they
finally got their hands on the code, after contacting the corresponding
author, it was only to realize that it could not be compiled and was mostly
unusable.\\

>>>>

\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-reproducibility are as diverse as the domains 
themselves. In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-reproducibility has been blamed on spurious p-value
claims (p-hacking), while in the biomedical sciences, \citep{iqbal:2016}
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor. Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception
despite the fact that they rely heavily on code and data that should
make them immune to the aforementioned problems.\\

When \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
  effort}. The results were dramatic: of the 515 (out of 613) potentially reproducible
papers targeted by the study, the authors managed to ultimately run
only 102 (i.e. less than 20\%). These low numbers figures reflect only the authors success at running the code. They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).  \citep{topalidou:2015a} encountered the same
problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section
of the paper and no link or repository was provided in the main text. When they
finally got their hands on the code, after contacting the corresponding
author, it was only to realize that it could not be compiled and was mostly
unusable.\\
